\bf Approximating Likelihood Ratios with Calibrated Discriminative Classifiers

### 2016-03-02 jasa/paper-jasa.tex
Spelling

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[height=12.5em]{figures/fig5a.pdf}
        \caption{True mean negative log-ratio}
        \label{fig:5a}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[height=12.5em]{figures/fig5b.pdf}
        \caption{Estimated mean negative log-ratio}
        \label{fig:5b}
    \end{subfigure}
    \caption{Inference from parameterized approximated likelihood ratios.
             (\ref{fig:5a}) True mean negative log-ratio for the observed data ${\cal D}$. The red dot corresponds to the nominal values $(A=1, B=-1)$, while the green dot is the maximum likelihood estimator $(\hat A=1.006, \hat B=-1.012)$.
             (\ref{fig:5b}) Estimated mean negative log-ratio, as approximated from the constructed objective by the gaussian process within the Bayesian optimization procedure. The blue dot is the estimated maximum likelihood estimator $(\hat A=0.956, \hat B=-0.869)$ while the white dots correspond to the points sampled during optimization.}
    \label{fig:5}
\end{figure}

@@

\section*{Acknowledgements} KC and GL are both supported through NSF ACI-1450310.
KC would like to thank Daniel Whiteson for
encouragement and Alex Ihler for challenging discussions
that  led to a reformulation of the initial idea. KC would also like to thank
Shimon Whiteson, Babak Shahbaba for advice in the presentation, Radford Neal for
discussion of his earlier work, Yann LeCun, Philip Stark, and Pierre Baldi for
their feedback on the project early in its conception, Bal\'azs K\'egl for
feedback to the draft,  and Yuri
Shirman for reassuring cross checks of the Theorem.   KC is grateful
to UC-Irvine for their hospitality while this research was carried out and the
Moore and Sloan foundations for their generous support of the data science
environment at NYU.

>>>>

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[height=12.5em]{figures/fig5a.pdf}
        \caption{True mean negative log-ratio}
        \label{fig:5a}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[height=12.5em]{figures/fig5b.pdf}
        \caption{Estimated mean negative log-ratio}
        \label{fig:5b}
    \end{subfigure}
    \caption{Inference from parameterized approximated likelihood ratios.
             (\ref{fig:5a}) True mean negative log-ratio for the observed data ${\cal D}$. The red dot corresponds to the nominal values $(A=1, B=-1)$, while the green dot is the maximum likelihood estimator $(\hat A=1.006, \hat B=-1.012)$.
             (\ref{fig:5b}) Estimated mean negative log-ratio, as approximated from the constructed objective by the Gaussian process within the Bayesian optimization procedure. The blue dot is the estimated maximum likelihood estimator $(\hat A=0.956, \hat B=-0.869)$ while the white dots correspond to the points sampled during optimization.}
    \label{fig:5}
\end{figure}

@@

\section*{Acknowledgments} KC and GL are both supported through NSF ACI-1450310.
KC would like to thank Daniel Whiteson for
encouragement and Alex Ihler for challenging discussions
that  led to a reformulation of the initial idea. KC would also like to thank
Shimon Whiteson, Babak Shahbaba for advice in the presentation, Radford Neal for
discussion of his earlier work, Yann LeCun, Philip Stark, and Pierre Baldi for
their feedback on the project early in its conception, Bal\'azs K\'egl for
feedback to the draft,  and Yuri
Shirman for reassuring cross checks of the Theorem.   KC is grateful
to UC-Irvine for their hospitality while this research was carried out and the
Moore and Sloan foundations for their generous support of the data science
environment at NYU.
